---
title: 'Googe Data Analysis Report'
author: 'Johannes Harmse'
output:
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>

# Google Data Visualisation
<br>

## Hypothesis
<br>

A Google user's browser history is dependent on his/her location due to having different interests when in different locations.
<br>
<br>

## Methodology
<br>

We are using two datasets to test this hypothesis. Each Google user has his/her own personal data collection from Google.
<br>
<br>

For this analysis we need a Google user's location and browser history datasets. This is easily obtainable from [Google Data](https://support.google.com/accounts/answer/3024190?hl=en).
<br>
<br>

We want to visually compare different time periods and locations movement for a given user to determine whether the user's Google most popular search words stay consistent or changes over time and location.
<br>
<br>

If you ran the following scripts, your visualisation should be displayed below.

* `../src/data_import.R`
<br>

* `../src/data_cleaning.R`
<br>

* `../src/data_visuaulisation.R`
<br>
<br>

## Results
```{r, echo = FALSE}
htmltools::includeHTML("anim.html")
```

## Conclusion
<br> 

From the visualisation, you should be able to conclude whether or not your searches stay the same over time across the location you have specified.
<br>
<br>

In general, it has been found that users' most popular searches vary a lot in frequency over time and location.
